\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-12-31 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_Rev1.tex
TPS  rebuttal round 1

The algorithmic appeal of the proximal recursion \eqref{ProxRecursionInfiniteDim} is that it opens up the possibility to compute the solution of the PDE initial value problem via recursive convex minimization. A point cloud-based proximal algorithm was proposed in \cite{caluya2019ACC,caluya2019TAC} which was reported to have very fast runtime. {\blue{The main idea in these references was to \emph{co-evolve} the time-varying state samples (via SDE discretization schemes such as the Euler-Maruyama method) as well as the joint PDF values (via \eqref{ProxRecursionInfiniteDim}) evaluated at those samples. The resulting computation is an \emph{online} propagation of the joint PDFs as opposed to the \emph{offline} computation in Monte Carlo or density estimation methods \cite{silverman1998density}. The latter methods only propagate the state samples and then approximate the joint PDFs as post-processing.}}

>>>>

The algorithmic appeal of the proximal recursion \eqref{ProxRecursionInfiniteDim} is that it opens up the possibility to compute the solution of the PDE initial value problem via recursive convex minimization. A point cloud-based proximal algorithm was proposed in \cite{caluya2019ACC,caluya2019TAC} which was reported to have very fast runtime. {\blue{The main idea in these references was to \emph{co-evolve} the time-varying state samples (via SDE discretization schemes such as the Euler-Maruyama scheme) as well as the joint PDF values (via \eqref{ProxRecursionInfiniteDim}) evaluated at those samples. The resulting computation is an \emph{online} propagation of the joint PDFs as opposed to the \emph{offline} computation in Monte Carlo or density estimation methods \cite{silverman1998density}. The latter methods only propagate the state samples and then approximate the joint PDFs as post-processing.}}
